\documentclass{article}

\usepackage{geometry}
\usepackage{indentfirst}
\usepackage{fancyhdr}
\usepackage{hyperref}

\pagestyle{fancy}
\geometry{a4paper, margin=1in}
\fancyhf{}
\fancyhead[C]{README / User Manual}
\fancyfoot[C]{\thepage}

\begin{document}

\title{README \\ \large Role-Based Internal Platform for Targeted Content Delivery}
\author{Group 20}
\date{December 5, 2025}

\maketitle

\section{Jira Project Link}

Project management and tasks are tracked in Jira:

\begin{itemize}
    \item Jira Board: \url{https://calstatela-cs3338-p6fsp1dk.atlassian.net/jira/software/projects/FN/boards/133}
\end{itemize}

\section{Objective}

The \textbf{Role-Based Internal Platform for Targeted Content Delivery} is an internal web application that:
\begin{itemize}
    \item Delivers announcements, policies, and training materials to employees.
    \item Uses roles, departments, and other attributes to decide which user sees which content.
    \item Tracks views and acknowledgements for mandatory content.
\end{itemize}

\section{Why This Software Matters}

The Platform is designed to improve:
\begin{itemize}
    \item \textbf{Productivity:} Users see a focused feed of content that is relevant to their role instead of generic email blasts.
    \item \textbf{Onboarding:} New employees can quickly find the required training and policies that are aimed at them.
    \item \textbf{Compliance:} Mandatory content can be tracked through acknowledgments and reports.
\end{itemize}

\section{How to Access the Platform}

For the purposes of this project, we assume the Platform is offered as a subscription-based internal product.

\subsection*{Production-Like Scenario (Conceptual)}

In a real deployment, an organization would:
\begin{itemize}
    \item Purchase a subscription from the official product website.
    \item Receive secure access to a hosted web URL (e.g., \texttt{https://portal.company-name.com}).
    \item Log in using organization credentials to access the Platform.
\end{itemize}

\subsection*{Course / Demo Setup}

For this course project:
\begin{itemize}
    \item The application runs locally using Docker or a local development server.
    \item The typical access URL is: \texttt{http://localhost:3000} (frontend) or as specified by the team.
    \item Test accounts (e.g., Employee, Manager, Admin) are documented in the project report or seeded in the database.
\end{itemize}

\section{Basic Usage Overview}

\begin{itemize}
    \item \textbf{Employees} log in to view their personalized content feed and acknowledge mandatory items.
    \item \textbf{Managers} can additionally view completion summaries for their team.
    \item \textbf{Content Administrators} create and schedule content and define targeting rules.
    \item \textbf{System Administrators} manage users, roles, and high-level configuration.
\end{itemize}

\end{document}
