\documentclass{article}

\usepackage{geometry}
\usepackage{indentfirst}
\usepackage{fancyhdr}
\usepackage{caption}
\usepackage{enumitem}
\usepackage[
    colorlinks=true,
    linkcolor=black,
    urlcolor=blue,
    citecolor=black
]{hyperref}
\usepackage{tabularx}

\pagestyle{fancy}
\geometry{a4paper, margin=1in}
\captionsetup{labelformat=empty}

\begin{document}

\title{Snapshot Objectives \\ \large Role-Based Internal Platform for Targeted Content Delivery}
\author{Version 1.0.0}
\date{
       Group 20
   \\ Jesus Calvo,
    \\ Justin Gip
    \\ Shane Guzman
    \\ Samuel Mekonnen
    \\ ------------------
    \\ December 5, 2025
    \\ CS 3338-01 (94305)
}

\maketitle
\newpage
\tableofcontents
\newpage

\fancyhf{}
\fancyhead[C]{Snapshot Objectives}
\fancyfoot[C]{\thepage}

\section{Introduction}

This document defines the objectives for each snapshot for the \textbf{Role-Based Internal Platform for Targeted Content Delivery}. Snapshots represent development milestones. Each snapshot includes:
\begin{itemize}
    \item Functional objectives (SRS requirements).
    \item Design and documentation deliverables.
    \item Testing objectives tracked using Jira.
\end{itemize}

\section{Snapshot 1 Objectives}

\subsection{Goal}
Establish the foundational architecture, implement basic authentication, and produce a minimal working interface. This snapshot validates that the system is functional.

\subsection{Functional Objectives}
\begin{itemize}
    \item Implement the user authentication workflow:
    \begin{itemize}
        \item Support login with email and password (FR-01, FR-02).
        \item Restrict access to authenticated pages (FR-03).
        \item Associate users with roles within the database (FR-04).
        \item Restrict administrative pages based on roles (FR-05).
    \end{itemize}
    \item Provide a simple post-login dashboard with placeholder content (precursor to FR-15).
\end{itemize}

\subsection{Design and Documentation Objectives}
\begin{itemize}
    \item Deliver initial versions of:
    \begin{itemize}
        \item Software Requirements Specification (SRS).
        \item Software Design Document (SDD).
        \item README / User Manual.
        \item Design Specification.
        \item Workflow Diagrams
    \end{itemize}
    \item Define the initial database schematic for \textit{User}, \textit{Role}, and \textit{UserRole}.
\end{itemize}

\subsection{Testing Objectives}
\begin{itemize}
    \item Create Jira test cases for:
    \begin{itemize}
        \item Login with valid credentials.
        \item Login with invalid credentials.
        \item Access control for protected routes.
    \end{itemize}
    \item Conduct manual smoke testing for the authentication flow.
\end{itemize}

\section{Snapshot 2 Objectives}

\subsection{Goal}
Introduce full content management and targeting rule capabilities, enabling administrators to create content and assign audiences based on user attributes.

\subsection{Functional Objectives}
\begin{itemize}
    \item Implement content management functionality (FR-06--FR-10):
    \begin{itemize}
        \item Create content items with title, body, categories, and tags.
        \item Specify start and end dates.
        \item Mark items as mandatory or optional.
        \item Edit and archive existing content.
    \end{itemize}
    \item Implement attribute-based targeting rules (FR-11--FR-14):
    \begin{itemize}
        \item Define rules using role, department, and location attributes.
        \item Support logical AND/OR combinations.
        \item Evaluate targeting rules at runtime.
        \item Update targeting evaluations when user attributes change.
    \end{itemize}
    \item Provide an \textbf{Admin Content List} and \textbf{Content Editor} UI.
\end{itemize}

\subsection{Design and Documentation Objectives}
\begin{itemize}
    \item Update the SDD with:
    \begin{itemize}
        \item Detailed design for the Content Management module.
        \item Targeting Engine architecture and data model updates.
    \end{itemize}
    \item Update the Design Specification with:
    \begin{itemize}
        \item Admin Content List page layout.
        \item Content Editor form fields and workflows.
    \end{itemize}
\end{itemize}

\subsection{Testing Objectives}
\begin{itemize}
    \item Create Jira test cases for:
    \begin{itemize}
        \item Creating content with valid and invalid data.
        \item Editing and archiving content.
        \item Creating and validating targeting rules.
        \item Ensuring visibility of content matches targeting criteria.
    \end{itemize}
\end{itemize}

\section{Snapshot 3 Objectives}

\subsection{Goal}
Deliver the full targeted content feed, user acknowledgement capabilities, and core analytics/reporting tools.

\subsection{Functional Objectives}
\begin{itemize}
    \item Implement targeted content feed features (FR-15--FR-19):
    \begin{itemize}
        \item Display only active, targeted content.
        \item Apply filters for categories and completion status.
        \item Provide search by title or keyword.
    \end{itemize}
    \item Implement acknowledgement and tracking features (FR-20--FR-23):
    \begin{itemize}
        \item Record content views.
        \item Allow acknowledgement of mandatory content.
        \item Prevent acknowledgement on behalf of another user.
    \end{itemize}
    \item Implement reporting features (FR-24--FR-26):
    \begin{itemize}
        \item Provide overview metrics for content.
        \item Provide team completion reporting for managers.
    \end{itemize}
\end{itemize}

\subsection{Design and Documentation Objectives}
\begin{itemize}
    \item Update SDD sections regarding:
    \begin{itemize}
        \item Delivery Service.
        \item Analytics and Reporting architecture.
        \item DeliveryEvent schema and aggregation logic.
    \end{itemize}
    \item Update the Design Specification to include:
    \begin{itemize}
        \item End User Dashboard.
        \item Content Detail Page.
        \item Reports Dashboard.
        \item Manager Team Completion view.
    \end{itemize}
    \item Update the README with user and admin workflows for content delivery and reporting.
\end{itemize}

\subsection{Testing Objectives}
\begin{itemize}
    \item Define Jira test cases for:
    \begin{itemize}
        \item Feed behavior across multiple roles and departments.
        \item Acknowledgement event tracking.
        \item Accuracy of reporting calculations.
    \end{itemize}
\end{itemize}

\section{Snapshot 4 Objectives}

\subsection{Goal}
Finalize administrative tools, improve nonfunctional aspects, and complete all documentation required for project delivery.

\subsection{Functional Objectives}
\begin{itemize}
    \item Implement full user and role management (FR-27--FR-30):
    \begin{itemize}
        \item Create, update, deactivate, and reactivate users.
        \item Assign and manage roles.
        \item Reset passwords.
        \item Log administrative changes.
    \end{itemize}
    \item Refine and polish previously implemented features:
    \begin{itemize}
        \item Improve UI/UX elements based on prior feedback.
        \item Add additional filters or search tools as needed.
    \end{itemize}
\end{itemize}

\subsection{Design and Documentation Objectives}
\begin{itemize}
    \item Finalize SRS and SDD:
    \begin{itemize}
        \item Ensure design and requirements reflect the implemented system.
        \item Complete revision histories and update traceability.
    \end{itemize}
    \item Finalize:
    \begin{itemize}
        \item Design Specification.
        \item README / User Manual (including Jira link).
        \item Snapshot Objectives (this document).
    \end{itemize}
\end{itemize}

\subsection{Testing Objectives}
\begin{itemize}
    \item Create a final Jira test cycle that:
    \begin{itemize}
        \item Tests all major system features end-to-end.
        \item Includes regression tests from earlier snapshots.
    \end{itemize}
\end{itemize}

\end{document}
